They are Very Smart: Genetic-Algorithm-Based Pathfinding in Games

### 2018-12-04 paper.tex
Paper: add pictures
Paper: add column width to image example
Add imfig macro
Paper: add more information to discussion, mainly problems

\usepackage{natbib,alifeconf}  %% The order is important
\usepackage{url}

@@

At this time, we are currently waiting on actual results from our project, but we hope that given a large enough population of zombies, we might see populations of zombies evolving to counteract players' strategies, although we may also see players coming up with ways to counteract the zombies by exploiting elements of the fitness function and construction system in ways unforeseen, possibly by playing in such a way as to allow the zombies to optimize for something other than killing the player's home base. Another possibility we might expect to see is the development of swarm or anti-swarm behavior based on the effectiveness of player defenses, as well as zombies possibly hitting minima or maxima depending on hard-coded numbers in the game environment.

In the future, we would experiment with elements such as variable damage output from towers and other defenses (so as to avoid the aforementioned numeric minima and maxima), as well as coming up with ways to encourage attacking the player's base more as time goes on.

Ultimately, we think that although evolution was the appropriate mechanism to to solve the issue at hand, game development was not the appropriate environment for this topic, given the time investment.

>>>>

\usepackage{natbib,alifeconf}  %% The order is important
\usepackage{url}
\usepackage{graphicx}
\graphicspath{ {./pictures/} }

@@

At this time, we are currently waiting on actual results from our project, but
we hope that given a large enough population of zombies, we might see
populations of zombies evolving to counteract players' strategies. Evolution
will likely have little trouble tackling a trivial or consistent player
strategy, like consistently rebuilding the same towers in the same place and
relying heavily on a single tower type, but evolution may have trouble keeping
up with a player that consistently changes strategy over the course of the game.
Our system of softmaxing the genome speed, health, and damage could also
result in progressively larger values relative to the mutation rate, making it
hard for long-evolved values to be changed in the face of changing player
strategies.

may also see players coming up with ways to counteract the zombies by exploiting
elements of the fitness function and construction system in ways unforeseen,
possibly by playing in such a way as to allow the zombies to optimize for
something other than killing the player's home base. Another possibility we
might expect to see is the development of swarm or anti-swarm behavior based on
the effectiveness of player defenses, as well as zombies possibly hitting minima
or maxima depending on hard-coded numbers in the game environment.

In the future, we could experiment with elements such as variable damage output
from towers and other defenses (so as to avoid the aforementioned numeric minima
and maxima), as well as coming up with ways to encourage attacking the player's
base more as time goes on; this could include ways
